\documentclass[../main.tex]{subfiles}

\begin{document}
  \chapter{Setup}
  Shuffle the Treasure, Loot, and Monster Decks. Also shuffle the Room Deck, if you are playing with it. Set aside space for a discard zone next to each of these decks.

  Decide on the number of ¢ in the game’s ¢ pool. This must be at least 100¢.

  Place the top two cards of the treasure deck face up next to it, forming two \textbf{shop slots}. These are the starting \textbf{shop items}.

  Place the top two cards of the Monster Deck face up next to it, forming two \textbf{monster slots}. Place any event cards (monster cards without a stat block; see \textbf{Card Types}) put in these slots during setup on the bottom of the deck and replace them with the top card of the Monster Deck. Repeat this until both monster slots have \textbf{monsters} in them.

  If you are playing with the Room Deck, place the top card of the Room Deck next to it, forming a \textbf{room slot}. That card will be the starting \textbf{room}.

  If you are playing with \textbf{bonus souls}, shuffle them, and pick 3 at random. Those 3 are the \textbf{active bonus souls} for the game and are placed face-up next to the play area.

  Deal a random character card to each player, as well as that character’s starting item card. Characters start the game \textbf{deactivated} (turned sideways). Starting items start the game \textbf{charged} (turned upright). Abilities that trigger at the start of the game trigger, for example Eden’s triggered ability. No one has \textbf{priority} here (see The Stack) and so these abilities will all resolve instantly.

  Deal 3 loot cards and 3¢ to each player. Each player puts the loot cards in their \textbf{hand}.

  Finally, you must decide on the starting player: the saddest player goes first! You can also each roll a dice (lowest roll goes first!) or use any other fair method of randomization, if you prefer. The game then starts, with the starting player taking the first turn.
\end{document}
